method

### 2021-10-08 06_Paper/ER-ED/method.Rmd
changed layout

_Part one: ER task._ <br>
Part one could be described as standard ER task that followed a block design (see Figure X), similar to paradigms previously used by our group [@Scheffel2021]. 
Participants were told to actively view neutral and negative pictures (see [2.4](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing and expressive suppression, respectively. 
Every participant first had the condition "active viewing-neutral" that served as a baseline condition.
During this block, 20 neutral pictures were presented.
Participants were asked to "actively view all pictures and permit all emotions that may arise."
In the second block, participants actively viewed negative pictures.
During the third, fourth, and fifth block, participants saw negative pictures and were asked to regulate their emotions using distraction, distancing, and suppression.
In order to achieve distraction, participants were asked to think of a geometric object or an everyday activity, like brushing their teeth.
During distancing, participants were asked to "take the position of a non-involved observer, thinking about the picture in a neutral way."
Participants were told not to re-interpret the situation or attaching a different meaning to the situation.
During suppression, participants were told to "suppress their emotional facial expression."
They should imagine being observed by a third person that should not be able to tell just by looking at the facial expression whether the person is looking at an emotional picture.
Participants were instructed not to suppress their thoughts or change their facial expression to the opposite [@Scheffel2021].
All participants received written instruction and completed a training session.
After the training session, participants were asked about their applied ER strategies to avoid misapplication.
The order of the three regulation blocks (distraction, distancing, and suppression) was randomized between participants.

_Part two: ER effort discounting._ <br>
In the second part, ER effort discounting took place.
The procedure of the discounting followed the COG-ED paradigm by Westbrook et al. [-@Westbrook2013] with major change.
We used the following adaption that allowed the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs. distancing, distraction vs. suppression, and distancing vs. suppression), two strategies with monetary values were presented.
The order of the comparisons was randomized.
Because there is no strategy that is objectively more difficult, we added an initial comparison that began with the option "1 EUR for strategy A or 1 EUR for strategy B".
The strategy that was not chosen was assigned the value 2 EUR.
From this point on, comparisons between strategies followed the original COG-ED paradigm [@Westbrook2013].
Participants were instructed to decide as realistically as possible, imaging the displayed money would really be up for election.

_Part three: ER choice._ <br>
After the discounting part, participants chose which of the three ER strategies (distraction, distancing or suppression) they wanted to reapply.
Importantly, there were no further instruction, on what basis they should make their decision.
Participants should make their decision freely, according to the criteria they considered important for themselves.
However, participants were asked to state the reasons for the decision afterwards.
As soon as they had decided, they saw the respective instruction. 
After, the block with another 20 negative pictures started.

@@

[...] <!-- Anne tried to implement a sentence here. -->

>>>>

*Part one: ER task.* <br>
Part one could be described as standard ER task that followed a block design (see Figure X), similar to paradigms previously used by our group [@Scheffel2021]. 
Participants were told to actively view neutral and negative pictures (see [2.4](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing and expressive suppression, respectively. 
Every participant first had the condition "active viewing-neutral" that served as a baseline condition.
During this block, 20 neutral pictures were presented.
Participants were asked to "actively view all pictures and permit all emotions that may arise."
In the second block, participants actively viewed negative pictures.
During the third, fourth, and fifth block, participants saw negative pictures and were asked to regulate their emotions using distraction, distancing, and suppression.
In order to achieve distraction, participants were asked to think of a geometric object or an everyday activity, like brushing their teeth.
During distancing, participants were asked to "take the position of a non-involved observer, thinking about the picture in a neutral way."
Participants were told not to re-interpret the situation or attaching a different meaning to the situation.
During suppression, participants were told to "suppress their emotional facial expression."
They should imagine being observed by a third person that should not be able to tell just by looking at the facial expression whether the person is looking at an emotional picture.
Participants were instructed not to suppress their thoughts or change their facial expression to the opposite [@Scheffel2021].
All participants received written instruction and completed a training session.
After the training session, participants were asked about their applied ER strategies to avoid misapplication.
The order of the three regulation blocks (distraction, distancing, and suppression) was randomized between participants.

*Part two: ER effort discounting.* <br>
In the second part, ER effort discounting took place.
The procedure of the discounting followed the COG-ED paradigm by Westbrook et al. [-@Westbrook2013] with major change.
We used the following adaption that allowed the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs. distancing, distraction vs. suppression, and distancing vs. suppression), two strategies with monetary values were presented.
The order of the comparisons was randomized.
Because there is no strategy that is objectively more difficult, we added an initial comparison that began with the option "1 EUR for strategy A or 1 EUR for strategy B".
The strategy that was not chosen was assigned the value 2 EUR.
From this point on, comparisons between strategies followed the original COG-ED paradigm [@Westbrook2013].
Participants were instructed to decide as realistically as possible, imaging the displayed money would really be up for election.

*Part three: ER choice.* <br>
After the discounting part, participants chose which of the three ER strategies (distraction, distancing or suppression) they wanted to reapply.
Importantly, there were no further instruction, on what basis they should make their decision.
Participants should make their decision freely, according to the criteria they considered important for themselves.
However, participants were asked to state the reasons for the decision afterwards.
As soon as they had decided, they saw the respective instruction. 
After, the block with another 20 negative pictures started.

@@

Electromyography (EMG) was recorded in the region of the *corrugator supercilii* and the *levator labii* at 1000 Hz sampling rate using Brain Vision Recorder (Brain Products Inc., Gilching, Germany).
Passive
[...] <!-- Anne tried to implement a sentence here. -->
